---
title: "YERBAS"
output: html_document
date: "2024-03-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(discrtr) # A companion package for the book Introduction to Discrete Choice Analysis with `R`
library(mlogit) # Multinomial Logit Models
library(readr) # Read Rectangular Text Data }

```

Invoke data set Mode from package mlogit. To do this you need to first load the package. This is a data set with choices about mode of transportation. This is done as follows:

```{r}
data("Mode")
```

Once you have loaded the data set, answer the following questions:
Describe this data set. How many variables are there and of which type (i.e., categorical/quantitative)?

```{r}
glimpse ("Mode")
```


How many different modes of transportation are in this data set? What is the most popular mode? What is the least popular mode?
```{r}
table (Mode$choice)
summary (Mode$choice) 

```

```{r}
ggplot(Mode)+
  geom_bar(aes(choice), color="red", fill= "#566AAA")

```


In general, what is the most expensive mode? The least expensive?
```{r}
summary(Mode)
```

```{r}
ggplot(Mode)+
  geom_density(aes(cost.car), color ="black", fill= "gold3", alpha=0.4)+
  geom_density(aes(cost.carpool), color ="black", fill= "pink3" , alpha=0.4)+
  geom_density(aes(cost.bus), color ="black", fill= "green" , alpha=0.4)+
  geom_density(aes(cost.rail), color ="black", fill= "purple" , alpha=0.4)


```


Create a plot showing the univariate distributions of time by car and time by bus. Discuss.

```{r}
ggplot(Mode)+
  geom_density(aes(cost.car), color ="black", fill= "gold3", alpha=0.4)+
  #geom_density(aes(cost.carpool), color ="black", fill= "red3" , alpha=0.4)+
  geom_density(aes(cost.bus), color ="black", fill= "green" , alpha=0.4)
  #geom_density(aes(cost.rail), color ="black", fill= "pink" , alpha=0.4)

```


How do choices relate to cost by the different modes?
```{r}
var_num <- names(Mode) [-1]
for (k in var_num) 
  {
  
  graf <- ggplot(Mode)+
  geom_boxplot(aes(choice, eval(as.name(k)), fill=choice), show.legend = FALSE) + 
  ylab(k)+ 
               
  theme_bw()
  
  print(graf)
}
```


